\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{OldStandard}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Michael Green} \\ \vspace{1pt}
    \small 1-250-540-9809 $|$ \href{mailto:greenmr1995@gmail.com}{\underline{greenmr1995@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/mrgreen95/}{\underline{linkedin.com/in/mrgreen95}} $|$
    \href{https://github.com/JackDuluoz}{\underline{github.com/JackDuluoz}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lighthouse Labs}{Vancouver, Can}
      {Diploma in Full Stack Web Development}{Oct 2022 -- Feb 2023}
    \resumeSubheading
      {Australian Institute of Business}{Adelaide, Aus}
      {Master of Business Administration (Finance)}{Jan 2020 -- Oct 2022}
    \resumeSubheading
      {Durham University}{Durham, UK}
      {Bachelor of Arts in History (Honours)}{Sep 2007 -- Jun 2010}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {1st Assistant Store Manager}{Feb 2019 -- Nov 2020}
      {Canada Safeway}{Vernon, BC}
      \resumeItemListStart
        \resumeItem{Profit centre generating annual revenue of CAD \$36,000,000 with over 150 unionised staff.}
        \resumeItem{Reduced labour costs by 5\% of sales. Increased YOY sales by 10\%. Achieved max bonus.}
        \resumeItem{Managed front line business during Covid when procedures were changing daily and anxieties were high.}
        \resumeItem{Duties: profit and loss management; planning, budgeting, and forecasting; customer escalation management; labour relations; community engagement; employee evaluation; hiring; payroll; food safety; health and safety.}
        \resumeItem{Cost-cutting and organisational restructuring eliminated back office support roles, pushing more responsibilities to store level. We eventually took on all administrative HR tasks and employee learning and development programs.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {2nd Assistant Store Manager}{Sep 2015 -- Feb 2019}
      {Canada Safeway}{Kelowna, BC}
      \resumeItemListStart
        \resumeItem{ASM with a focus on the grocery department, which accounted for 50\% of store sales and 66\% of store real estate.}
        \resumeItem{The Downtown Kelowna location ranked first for sales per square foot in interior BC and top three for tonnage despite having the smallest backroom and sales floor. This required expert organisation, time management, and productivity.}
        \resumeItem{Key responsibilities: inventory management; sales and merchandising; shrinkage; loss prevention; scheduling.}
    \resumeItemListEnd

    \resumeSubheading
      {Management Trainee}{Sep 2013 -- Sep 2015}
      {Canada Safeway}{Banff, AB}
      \resumeItemListStart
        \resumeItem{Completed Mentoring for Career Development (MCD) internal training program in core functions of the business.}
        \resumeItem{Appointed store Change Agent following acquisition by Sobeys: Having mastered legacy Safeway systems, I received advanced training in the new Sobeys systems in order to lead the retraining of Safeway staff.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/JackDuluoz/RentProof}{\textbf{\underline{RentProof}}} $|$ \emph{React, SCSS, Google Maps API, Node/Express, PostgreSQL}}{Feb 2023}
          \resumeItemListStart
            \resumeItem{Renters post price updates for their property with supporting documentation, to be approved by site admin.}
            \resumeItem{Over time this contributes to a detailed price history of individual properties and market trends.}
            \resumeItem{Intuitive and dynamic map markers load property price data when clicked.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/JackDuluoz/jungle-rails}
          {\textbf{\underline{The Jungle}}} $|$ \emph{Ruby on Rails, PostgreSQL, RSpec, Cypress}}{Jan 2023}
          \resumeItemListStart
            \resumeItem{An e-commerce application built with Rails 6.1. Payments processed using Stripe.}
            \resumeItem{Integration tested with RSpec and end-to-end tested with Cypress.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/JackDuluoz/scheduler}
          {\textbf{\underline{Scheduler}}} $|$ \emph{React, SCSS, Node/Express, PostgreSQL, Storybook, Jest, Cypress}}{Jan 2023}
          \resumeItemListStart
            \resumeItem{A full-stack, single-page appointment scheduling tool connecting students with mentors.}
            \resumeItem{Components built and tested with Storybook.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Working Knowledge}{: JavaScript, TypeScript, HTML, CSS, SCSS, React, Material-UI, Angular, Angular Material, Node.js, Express, SQL (Postgres), MongoDB, Google Maps API, Git (GitHub), Linux, VS Code, LaTeX} \\
     \textbf{Exposure}{: Ruby, Rails, EJS, jQuery, Ajax, Figma, Tailwind, Storybook, Cypress, Jest, Mocha, Chai, RSpec} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
