%-------------------------
% Resume in Latex
% Author: Michael Green
% Based on: https://github.com/sb2nov/resume and Jake Gutierre's template
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Michael Green} \\ \vspace{2pt}
    \small
    \href{https://www.linkedin.com/in/mrgreen95/}{\underline{linkedin.com/in/mrgreen95}} \hspace{2pt} $|$ \hspace{2pt}
    \href{https://github.com/JackDuluoz}{\underline{github.com/JackDuluoz}} \hspace{2pt} $|$ \hspace{2pt}
    \href{https://jackduluoz.github.io/portfolio/}
    {\underline{michaelgreen.ca}}
    \\ \vspace{2pt}
    \small 1-250-540-9809 \hspace{4pt} $|$ \hspace{4pt} 
    \href{mailto:greenmr1995@gmail.com}{\underline{greenmr1995@gmail.com}} \hspace{4pt} $|$ \hspace{4pt}    
    \small Vernon, BC, Canada
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lighthouse Labs}{Vancouver, Can}
      {Diploma in Full Stack Web Development}{Oct 2022 -- Feb 2023}
    \resumeSubheading
      {Australian Institute of Business}{Adelaide, Aus}
      {Master of Business Administration (Finance)}{Jan 2020 -- Oct 2022}
    \resumeSubheading
      {Durham University}{Durham, UK}
      {Bachelor of Arts in History (Honours)}{Sep 2007 -- Jun 2010}
  \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Working Knowledge}{: JavaScript, TypeScript, HTML, CSS, SCSS, React, Angular, Angular Material, Node.js, Express, SQL (Postgres), Google Maps API, Linux (Ubuntu), Git (GitHub), VS Code} \\ \vspace{1.5pt}
     \textbf{Exposed To}{: Ruby on Rails, Python, LaTeX, MongoDB, EJS, jQuery, Ajax, Figma, Tailwind, Material-UI, Storybook, Cypress, Jest, Mocha, Chai, RSpec} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {1st Assistant Store Manager}{Feb 2019 -- Nov 2020}
      {Canada Safeway}{Vernon, BC}
      \resumeItemListStart
        \resumeItem{Oversaw daily operations at a retail profit centre generating annual {\textbf{revenues of \$36,000,000}}.}
        \resumeItem{Responsible for {\textbf{150 unionised staff}} across {\textbf{10 departments}} operating 24 hours a day.}
        \resumeItem{Reduced labour costs by 5\% of sales. Increased YOY sales by 10\%. Achieved max bonus.}
        \resumeItem{Managed a front line business during Covid when procedures were changing daily and anxieties were high.}
        \resumeItem{Cost-cutting and restructuring eliminated back office support roles, pushing responsibilities to store level. We absorbed administrative HR functions, employee L\&D programs, and continued operations without specialist support.}
        \resumeItem{Duties: profit and loss management; planning, budgeting, and forecasting; customer escalation management; labour relations; community engagement; employee evaluation; hiring; payroll; food safety; health and safety (compliance).}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {2nd Assistant Store Manager}{Sep 2015 -- Feb 2019}
      {Canada Safeway}{Kelowna, BC}
      \resumeItemListStart
        \resumeItem{ASM accountable for the grocery department, which comprised 50\% of store sales and 66\% of store real estate.}
        \resumeItem{This location {\textbf{ranked first}} for sales per square foot in interior BC and top three for tonnage despite having the smallest backroom and sales floor. We were {\textbf{process driven}} experts in organisation, time management, and productivity.}
        \resumeItem{Duties: team leadership; scheduling; inventory management; sales and merchandising; shrinkage; loss prevention.}
    \resumeItemListEnd

    \resumeSubheading
      {Management Trainee}{Sep 2013 -- Sep 2015}
      {Canada Safeway}{Banff, AB}
      \resumeItemListStart
        \resumeItem{Completed Mentoring for Career Development (MCD) internal training program in core functions of the business.}
        \resumeItem{Appointed store {\textbf{Change Agent}} following acquisition by Sobeys: Having mastered legacy Safeway systems, I received advanced training in the new Sobeys systems in order to lead the retraining of Safeway staff.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{RentProof} $|$ 
          \href{https://github.com/JackDuluoz/RentProof}
          {\underline{github/RentProof}} $|$
          \emph{React, SCSS, Google Maps API, Node/Express, PostgreSQL}}{Feb 2023}
          \resumeItemListStart
            \resumeItem{Renters post price updates for their property with supporting documentation, to be approved by site admin.}
            \resumeItem{Over time this contributes to a detailed price history of individual properties and market trends.}
            \resumeItem{Intuitive and dynamic map markers load property price data when clicked.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Scheduler} $|$ 
          \href{https://github.com/JackDuluoz/scheduler}
          {\underline{github/Scheduler}} $|$
          \emph{React, SCSS, Node/Express, PostgreSQL, Storybook, Jest, Cypress}}{Jan 2023}
          \resumeItemListStart
            \resumeItem{A full-stack, single-page appointment app connecting students with mentors.}
            \resumeItem{Components built and tested with Storybook.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Jungle} $|$ 
          \href{https://github.com/JackDuluoz/jungle-rails}
          {\underline{github/Jungle}} $|$
          \emph{Ruby on Rails, PostgreSQL, RSpec, Cypress}}{Jan 2023}
          \resumeItemListStart
            \resumeItem{An e-commerce application built with Rails 6.1. Payments processed using Stripe.}
            \resumeItem{Integration tested with RSpec and end-to-end tested with Cypress.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
